|

### 2023-04-11 appendix.Rmd
replace with calculated numbers

```{r}
# Calculate these numbers
matrix(c(c(576, 0, 144, 0, 540, 135, 1116),
         c(2880, 0, 864, 0, 2700, 810, 7254),
         c(160, 0, 123, 0, 160, 123, 443)),
       ncol = 7,
       byrow = TRUE) %>%
  data.frame() %>%
  add_column(name = c("Lineups", "Evaluations", "Participants"), .before = 1) %>%
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE,
                    label = "count-lineup",
                    caption = "Count of lineups, evaluations and participants over departure types and data collection periods.",
                    col.names = c("Number", "I", "II", "III", "I", "II", "II", "Total")) %>%
  kableExtra::add_header_above(c(" " = 1, "Non-linearity" = 3, "Heteroskedasticity" = 3))
```

>>>>

```{r}
# Calculate these numbers
a1 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 3) %>%
  count(unique_lineup_id) %>%
  nrow()

a2 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 4) %>%
  count(unique_lineup_id) %>%
  nrow()

a3 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 5) %>%
  count(unique_lineup_id) %>%
  nrow()

a4 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 3) %>%
  count(unique_lineup_id) %>%
  nrow()

a5 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 4) %>%
  count(unique_lineup_id) %>%
  nrow()

a6 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 5) %>%
  count(unique_lineup_id) %>%
  nrow()

a7 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  count(unique_lineup_id) %>%
  nrow()

b1 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 3) %>%
  nrow()

b2 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 4) %>%
  nrow()

b3 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 5) %>%
  nrow()

b4 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 3) %>%
  nrow()

b5 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 4) %>%
  nrow()

b6 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 5) %>%
  nrow()

b7 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  nrow()

c1 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 3) %>%
  count(set) %>%
  nrow()

c2 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 4) %>%
  count(set) %>%
  nrow()

c3 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  filter(exp == 5) %>%
  count(set) %>%
  nrow()

c4 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 3) %>%
  count(set) %>%
  nrow()

c5 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 4) %>%
  count(set) %>%
  nrow()

c6 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type != "polynomial") %>%
  filter(exp == 5) %>%
  count(set) %>%
  nrow()

c7 <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  count(exp, set) %>%
  nrow()

matrix(c(c(a1, a2, a3, a4, a5, a6, a7),
         c(b1, b2, b3, b4, b5, b6, b7),
         c(c1, c2, c3, c4, c5, c6, c7)),
       ncol = 7,
       byrow = TRUE) %>%
  data.frame() %>%
  add_column(name = c("Lineups", "Evaluations", "Participants"), .before = 1) %>%
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE,
                    label = "count-lineup",
                    caption = "Count of lineups, evaluations and participants over departure types and data collection periods.",
                    col.names = c("Number", "I", "II", "III", "I", "II", "II", "Total")) %>%
  kableExtra::add_header_above(c(" " = 1, "Non-linearity" = 3, "Heteroskedasticity" = 3))
```
